\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
     I would like to thank Professor Takashi Onaka firstly for guiding me through this difficult project. From the start, the AME to PAH investigation has been a daunting one, and I have had to learn a very wide range of new skills to compile this thesis. Onaka-sensei deserves many thanks for challenging me to work on such a project, and somehow remaining extremely helpful while still pushing me to solve problems autonomously. Somehow I have survived long enough to fix many of my earlier mistakes and to correct many misconceptions (though I still have much to learn, and look forward to doing so). This is not only true in my research, but in learning how to survive in Japan. Onaka-sensei and the members of the Onaka-lab have literally helped me to survive here, assisting any time that I have had difficulty adjusting as a foreign student. Tamami Mori, objectively determined to be the greatest senpai ever, has given me much moral support, scientific advice (especially relating to this thesis), and has rescued me many times from University policies which I was unable understand myself. Kazuki Sato has demonstrated some magical ability to both assist me in daily struggles in Japanese life and the masters course, while also dutifully preparing his own masters course thesis. You have been a great classmate, thank you. \\
     Our group's assistant professor, Itsuki Sakon has helped me greatly from the moment I arrived in Japan, literally. From picking me up at Narita upon my first arrival to helping me find an apartment when my dormitory term expired, to offering prompt and thorough feedback about my project even though he is not my supervisor. It is also quite refreshing when his driving skills leave me at my destination much earlier than planned.\\
     Special thanks is owed to the post-docs of our lab, who have no responsibility to assist a ``fresh" astronomy grad-student like myself, but still enthusiastically share their research experience and moral support. Before Ronin Wu arrived in our lab, I had very little motivation to develop my extremely limited programming knowledge. With her direct encouragement and criticism I was able to follow through with the intimidating task of handling all of the data in a streamlined way. Her invitations to tea-time were another critical component to this investigation.\\
     Mark Hammonds always has the right feedback in order to break tunnel vision. Discussion with him over this year and a half helped me keep my scientific imagination stimulated and remind me not to be negligent about the chemistry of interstellar space. Small plastic dinosaurs and storm troopers occasionally left on my desk provide further encouragement. \\
     Fumihiko Usui has a talent for introducing me to the right people whenever I need help with the FIS data. Also, he gives me motivation to continue researching astronomy, in that I too one day hope to have an asteroid named after me.
     Members of the FIS team have always been kind and supportive of my studies. Espeically Takafumi Ootsubo and Yasuo Doi who kindly serves data analysis and IDL tips along with a freshly ground cup of drip coffee at each of our visits.\\
     I have been very lucky to have helpful co-authors for the various posters and abstracts I have presented in the course of this thesis. Ho-Gyu Lee, Martin Giard, Daisuke Ishihara, and Yasuo Doi somehow find time to share their advice before each deadline. Ho-Gyu Lee especially has given me much feedback both before and after he moved from Todai to KASI. I enjoy running into him in various parts of the world, and hope this trend continues. In writing this thesis, I have been fortunate to receive very insightful, efficient, and friendly advice from my reviewer, Professor Raffaele Flaminio.\\
     My undergraduate advisor, Steven Gibson, deserves a special thanks for continued kind encouragement and research advice even now that I have graduated from WKU. His guidance while I was a student at the Gatton Academy at WKU and later at the WKU Honors College gave me the motivation to study astrophysics further, and helped me build a foundational understanding of research. And not secondary to that, he is always happy to share his frank advice about life. This was something I really needed when I was deciding what to do with my life's story after graduating from WKU.\\ 
     Jonathan Newton, who was part of Dr. Gibson's undergraduate research group at WKU, has also been very kind to offer advice over the last few years (even though he has been very busy with his own master's course thesis). More importantly, he is always happy to share a joke or two about the silliness of certain IDL routine names.\\
     Others at WKU were incredibly helpful to my while I was applying to graduate programs and scholarships, including the one I have just graduated. Especially Audra Jennings, the Director of the Office of Scholar Development. She is one of the very dedicated people at WKU who cares about the development of each student, even if their field is different from hers. I could not have made it here, or to many other experiences such as my astrobiology course in Brazil without support from her and WKU. Further thanks to those at the Center for Gifted Studies and the Gatton Academy for helping me start this adventure. \\
     Most personally, I must thank my mother, Catherine Marie Bell who has supported me more than seems possible for a single human being. Despite my moving away to the other side of the world, she still keeps me going via e-mails and our poorly connected Skype conversations as I stroll around Sanshiro Ike. She has already given up so much time with me, and I hope I can somehow repay it when I finish my studies. The same goes to my younger siblings, Joseph, Emma, Caleb, and Noah who I have too few opportunities to help grow up, but who still encourage me whenever I return home. They are finding their own way, which seems very different from my path as an astronomer, but I am still proud of them in every way. I am always learning from them, especially my sister Emma who keeps me well-updated about sheep.\\
     While my family is unfortunately far away, my day to day life in Japan has been strongly supported by my good friend, Yuki Sugisawa \begin{CJK}{UTF8}{min}(杉澤友紀)\end{CJK}. Thanks to him I have a collection of very positive memories even for the times when my studies are the most challenging. As a side note, he makes the best takoyaki. Not only Yuki, but his mother Chikako \begin{CJK}{UTF8}{min}(千賀子様), sister Hiromi (宏美様), and father Takeshi (剛様)\end{CJK} who have been like a host family to me in these last two years. Even his grandmother Junko  and grandfather Sadao Masuda \begin{CJK}{UTF8}{min}(桝田順子と定雄様)\end{CJK} have shown me much kindness during my visits to Osaka. I never could have hoped to have been "adopted" in this way. \begin{CJK}{UTF8}{min}おおきにありがとうございました.\end{CJK}\\
     A special note of thanks is deserved by a special group of people who have inspired me and shared moral support throughout my entire university life. My friends from the Gatton Academy community who have kept in touch regularly even since my moving to Japan, help me keep a wider perspective on my life beyond simply my current research topic. Discussions with them about physics, biology, computer science, psychology, art, science fiction, language, life, and especially food always leave me inspired and encouraged. Special thanks to Alexandria Boswell, Alexander Chen, George Johnson, Hannah Kagan-Moore, Jay Ludden, and John Max Wilson.\\
     My financial support for living and tuition expenses during this time has been generously provided by "MEXT", the Ministry of Education, Culture, Sports, Science and Technology (\begin{CJK}{UTF8}{min}文部科学省.\end{CJK}). \\
     This research is based on observations with AKARI, a JAXA project with the participation of ESA; Planck (http://www.esa.int/Planck), an ESA science 
mission with instruments and contributions directly funded by ESA Member States, NASA, 
and Canada; and IRAS, a joint project of the US, UK and the Netherlands.